Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-07-06 paper/JMNotes.Rmd
add note on Figure 7
add notes on CAST

>>>>

- Figure 7: spatial tiling. 
It would be great if one could see the used rectangular blocks.
- Figure 9: in fact, one only sees 4 time levels, not 5 as stated in the caption
- LLTO: maybe you could expand a little bit on why observations need to be omitted.
For readers new to the LLTO concept, the reasoning for this might not be entirely clear.
